Improving \textsl{Gaia} parallaxes with a data-driven model \\ of the color--magnitude diagram

### 2017-06-02 paper/paper.tex
fixed git issue

  Beyond this, the choice of the Gaussian form itself for the mixture is
  questionable. The Gaussian has great properties, that we capitalize on
  both at the prior-generation stage (with \xd), and at the photometric-parallax
  stage (capitalizing on Gaussian product rules). We could move to other
  forms, but they would be extremely expensive, computationally.
\item[no physics] Although it is presented as an advantage of our
  method that we never make any use of physical models, it is also
  brings some significant disadvantages: For example, the 
\end{description}

>>>>

  Beyond this, the choice of the Gaussian form itself for the mixture is
  questionable. The Gaussian has great properties, that we capitalize on
  both at the prior-generation stage (with \xd), and at the photometric-parallax
  stage (capitalizing on Gaussian product rules). We could move to other
  forms, but they would be extremely expensive, computationally.
\item[no physics] Although it is presented as an advantage of our
  method that we never make any use of physical models, it is also
  brings some significant disadvantages: For example, the \cmd\ contains
  features that are obvious products of stellar evolution, but doesn't in
  itself inform the theory or models of stellar evolution, because our
  mixture-of-Gaussian \cmd\ model is divorced from any theoretical ideas
  about stars. For another, stellar evolution models are in fact very
  predictive and successful; our model does not capitalize in any way on
  those successes. A next-generation model might be designed to be data-driven
  but nonetheless capitalize on physics-driven successes. One framework
  for that would be to fit not the \cmd\ but rather deviations of the \cmd\ away
  from a good physics-based model prediction.
\end{description}
